PInSoRo: A Dataset for Deep-learning of Human-Robot Social Interactions

### 2017-06-27 paper.tex
Section on data post processing

As the data is recorded using ROS's bag files, it can be replayed in the exact
same conditions as it was during the recording. All the video streams use
calibrated cameras. Only the raw RGB and depth video streams are recorded. While
the raw RGB and depth streams are neither rectified nor registered together (due
to performance considerations during the recording), it can be easily achieved
as a post-process step, using standard ROS tools (the ROS {\tt rgbd\_pipeline}).
Pre-configured scripts are available alongside the dataset\footnote{Available
online from
\url{https://github.com/severin-lemaignan/freeplay-sandbox-analysis}.} to
republish registered streams and the corresponding 3D point-clouds (as seen in
Fig.~\ref{fig|rviz}, left).

@@

\subsubsection{Conditions}\label{conditions}

\begin{itemize}
\item
  Condition A: one pair of children play freely  simultaneously on the
  sandtray.
\item
  Condition B: one child plays on the sandtray with the robot. The robot does
  not exhibit any social behaviour.
\end{itemize}

\subsubsection{Demographics}\label{demographics}

\begin{itemize}
\item
  Condition A: 40 pairs of children (i.e., 80 children)
\item
  Condition B: 40 children
\end{itemize}

@@

\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.4\linewidth]{setup_child_child_top}
    \hspace{1.5cm}
    \includegraphics[width=0.4\linewidth]{setup_child_robot_top}
    \caption{Experimental setup, child-child condition (left) and child-robot
    condition (right).}
    \label{fig|setup}
\end{figure}

The interaction is recorded by 3 cameras: one `environment' camera
filming the whole scene and two RGB-D cameras, one focused on each of the
children's faces. Audio is recorded using the microphones integrated to the RGB-D cameras.

One computer (integrated with the touchscreen) manages the game and the
synchronous recording of the cameras and microphones.

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Welcome (5 min):

@@

>>>>

As the data is recorded using ROS's bag files, it can be replayed in the exact
same conditions as it was during the recording. All the video streams use
calibrated cameras. Only the raw RGB and depth video streams are recorded.

@@

\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.8\linewidth]{setup_child_child_top}
    %\hspace{1.5cm}
    %\includegraphics[width=0.4\linewidth]{setup_child_robot_top}
    %\caption{Experimental setup, child-child condition (left) and child-robot condition (right).}
    \caption{Experimental setup}
    \label{fig|setup}
\end{figure}

@@

@@

\begin{enumerate}
\item
  Welcome (5 min):

@@

\subsection{Data post-processing}

While
the raw RGB and depth streams are neither rectified nor registered together (due
to performance considerations during the recording), it can be easily achieved
as a post-process step, using standard ROS tools (the ROS {\tt rgbd\_pipeline}).
Pre-configured scripts are available alongside the dataset\footnote{Available
online from
\url{https://github.com/severin-lemaignan/freeplay-sandbox-analysis}.} to
republish registered streams and the corresponding 3D point-clouds (as seen in
Fig.~\ref{fig|rviz}, left).

Using the {\tt gazr} face tracking library\footnote{Available online from
\url{https://github.com/severin-lemaignan/gazr}. {\tt gazr} relies on the {\tt
dlib} face tracker for facial features
extraction.}~\cite{lemaignan2016realtime}, children faces and facial features can
are extracted and reprojected onto the 3D point-clouds (Fig.~\ref{fig|rviz},
right). Faces have been successfully detected in 57\% of the recorded frames
in the dataset. Undetected faces are due to occlusions (the child put her arm in
front of the camera), large head rotations or quick child motion.
